Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-23 paper/paper.tex
Fix issues and typos

The first extension to the Go tool we created would be to add support for Bugzilla. We already achieved this 
when we were first prototyping the application, but we decided to proceed exclusively with Jira mainly because 
the APIs proved to be more reliable and also versatile in terms of what data you could collect. Another 
reason was that we were time retricted, thus we wanted to have first a well tested and stable solution for Jira and 
only after add support for other issue tracking systems. However, we already prepared for other potential systems by 
adding interfaces for tickets and REST clients, making Bugzilla, Manuscript, YouTrack or any 
other issue tracking system straightforward to add to the application.

@@

There is also room for future work in terms of the data collected. Even though the database we collected 
is large, there is never enough tickets to analyse. Thus, the store command of the tool could be run against 
other Jira instances apart from Apache's and collect tickets from other projects, thus improving the diversity 
and the total number of tickets to be analysed. As we did not have access to any cluster or virtual machines in 
the cloud, we ran all our analyses on local machines (laptops) and it could still take well over two hours to complete 
with over 10 GB of RAM and 70\% CPU in usage.

@@

Another aspect that could be improved is having access to funds in order to buy Google Cloud Platform credits. This 
would be required to use the Natural Language Processing APIs on large amounts of data. We used the credits provided 
in the free trial but quickly ran out completely after only 160,000 tickets. Also, credits on Microsoft Azure would 
prove useful as their Spell Check API is the most efficient at the moment.

@@

We manager to answer all seven research questions and find factors that can posittively or 
negatively affect the \emph{Time-To-Close} value of a ticket. All of our results are statistically significant and we can summarise 
them as follows:
\begin{itemize}
  \item the presence of steps to reproduce reduces the \emph{Time-To-Close} for a ticket;
  \item the presence of stack traces reduces the \emph{Time-To-Close} for a ticket;
  \item the presence of attachments reduces the \emph{Time-To-Close} for a ticket - more specifically tickets with screenshots, 
  config files or text files help tickets get closed quicker than those without attachments;
  \item higher numbers of grammar errors imply increased \emph{Time-To-Close} values;
  \item higher sentiment scores imply reduced \emph{Time-To-Close} values for a ticket;
  \item higher numbers of words in comments imply increased \emph{Time-To-Close} values for a ticket;
  \item higher number of words in description and summary increase the \emph{Time-To-Close} values for tickets.
\end{itemize}

@@

\vskip8pt \noindent
{\bf Acknowledgments.}
I would first like to thank Dr. Storer for the amazing work he has put in helping me go through with finishing 
this project. I would definitely not have been able to achieve what we've achieved with any other supervisor, so 
thank you, Tim, for all the support, kindness and advice you have given me throughout this academic year. I would 
also like to thank you for being the lecturer who has taught me the most throughout all my years at the university
and whose advice and ideas I have applied at all my work places and my personal projects.

The next huge thank you would have to go to my parents, the most amazing family in the world! Without them I would 
not be here and I wouldn't have had anything of what I have now, both personally and professionally. 
I will always treasure the unconditional support you have always offered me! Thank you for being my parents, Mom and Dad!

And last but not least, I want to thank my partner in \"crime\" and in life, Corina! Without her, I would not be who I 
am today. You have been with me through thick and thin, in both bad moments (such as the endless nights working 
on ticket statistics) and best moments in my life! Thank you for everything! I will always love you!

>>>>

The first extension to the Go tool we created would be to add support for Bugzilla. We already achieved this 
when we were first prototyping the application, but we decided to proceed exclusively with Jira mainly because 
the APIs proved to be more reliable and also versatile in terms of what data could be collected. Another 
reason was that we were time restricted, thus we wanted to have first a well tested and stable solution for Jira and 
only after add support for other issue tracking systems. However, we already prepared for other potential systems by 
adding interfaces for tickets and REST clients, making Bugzilla, Manuscript, YouTrack or any 
other issue tracking system straightforward to add to the application.

@@

There is also room for future work in terms of the data collected. Even though the database we collected 
is large, there are never too many tickets to analyse. Thus, the store command of the tool could be run against 
other Jira instances apart from Apache's and collect tickets from other projects, thus improving the diversity 
and the total number of tickets to be analysed. As we did not have access to any cluster or virtual machines in 
the cloud, we ran all our analyses on local machines (laptops) and it could still take well over two hours to complete 
with over 10 GB of RAM and 70\% CPU in usage.

@@

Another aspect that could be improved is allocating a budget for Google Cloud Platform credits. This 
would be required for running the Natural Language Processing APIs on large amounts of data. We used the credits provided 
in the free trial but quickly ran out completely after only 160,000 tickets. Also, credits on Microsoft Azure would 
prove useful as their Spell Check API is the most efficient at the moment.

@@

We managed to answer all seven research questions and find factors that can positively or 
negatively affect the \emph{Time-To-Close} value of a ticket. All of our results are statistically significant and we can summarise 
them as follows:
\begin{itemize}
  \item the presence of steps to reproduce reduces the \emph{Time-To-Close} for a ticket;
  \item the presence of stack traces reduces the \emph{Time-To-Close} for a ticket;
  \item the presence of attachments reduces the \emph{Time-To-Close} for a ticket - more specifically tickets with screenshots, 
  config files or text files help tickets get closed quicker than those without attachments;
  \item higher numbers of grammar errors imply increased \emph{Time-To-Close} values;
  \item higher sentiment scores imply reduced \emph{Time-To-Close} values for a ticket;
  \item higher numbers of words in comments imply increased \emph{Time-To-Close} values for a ticket;
  \item higher number of words in description and summary increase the \emph{Time-To-Close} values for tickets.
\end{itemize}

@@

\vskip8pt \noindent
{\bf Acknowledgments.}
I would first like to thank Dr. Storer for the amazing work he has put in helping me go through with finishing 
this project. I would definitely not have been able to achieve what we've achieved with any other supervisor, so 
thank you, Tim, for all the support, kindness and advice you have given me throughout this academic year. I would 
also like to thank you for being the lecturer who has taught me the most throughout all my years at university
and whose advice and ideas I have applied in all my work places and my personal projects.

The next huge thank you would have to go to my parents! Without them I would 
not be here and I wouldn't have accomplished so much, both in my personal and professional lives. 
I will always treasure the unconditional support you have offered me! Thank you for being the parents that you are!

And last but not least, I want to thank my partner in "crime" and in life, Corina! Without her, I would not be who I 
am today. You have been with me through thick and thin, in both bad moments (such as the endless nights working 
on ticket statistics) and best moments in my life! Thank you for everything!
